Verifying Spatial Properties of Array Computations

### 2017-04-14 oopsla17/oopsla17.tex
Further explain derived induction vars

  A \emph{derived induction variable} is an expression of the form $a
  i + b$, \ie{}, an affine expression on an induction variable $i$.
\end{defn}

>>>>

  A \emph{derived induction variable} is an expression of the form $a \times i
  + b$, where $a$ and $b$ are constant expressions, \ie{}, an affine expression
  on an induction variable $i$.
\end{defn}
